Extending the WebID Protocol with Access Delegation

### 2012-07-31 paper.tex
update abstract

\usepackage[
pdftex,
bookmarks=true,
%hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}

@@

\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}}

@@

\begin{abstract}
We propose \ldots
\end{abstract}

>>>>

\usepackage[
pdftex,
bookmarks=true,
%hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}

@@

\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Michael Martin\inst{1} \and S\"oren Auer\inst{1}}

@@

\begin{abstract}
The WebID protocol enables the global identification of agents in a distributed manner by employing asymmetric cryptography and Linked Data principles.
WebIDs are mostly used in scenarios where a user utilize a browser application to access a protected resource on a web server.
In order to decide whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and resources which contain relationship information between agents and other related information.
%Currently, those information needs to be publicly available, which leads to an privacy issue, since agents may want to hide such information from the general audience.
In this paper we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g. a server application.
This extends the range of application scenarios where WebID authentication can be deployed to all kinds of server to server resource consumption scenarios and other use cases.  
\end{abstract}
